Twists of supersymmetric gauge theories

### 2019-08-06 paper.tex
Started some notes on 9d, also some minor rearrangements and comments
Added some comments on proving supersymmetry for SYM

\begin{prop}
Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra \chris{we'll have to see whether we want Poincar\'e or just translation here}. The functional
\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
satisfies the Maurer-Cartan equation
\begin{equation} 
\label{10d_MC}
(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
\end{equation}
\end{prop}

@@

First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.  First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.  Then \ref{10d_MC_1} is zero by Baez--Huerta.  Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}. Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.  Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}
\end{proof}

@@

>>>>

\begin{prop}
Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra \chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.  On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.  To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}. The functional
\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
satisfies the Maurer-Cartan equation
\begin{equation} 
\label{10d_MC}
(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
\end{equation}
\end{prop}

@@

First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.  First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.  Then \ref{10d_MC_1} is zero by Baez--Huerta.  Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}. Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.  Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}

\chris{apart from the Lemma \ref{10d_onshell_lemma}, this is all completely identical for dimensions 3,4,6,10.  Even that lemma only uses abstract gamma matrix manipulations that work in any dimension along with the Baez Huerta rule that applies in those dimensions, so I think we should just state a single result valid for those four theories simultaneously.}
\end{proof}

@@

\subsection{Twisting Homomorphisms and Curved Backgrounds}
